---
title: "Business Data Science Basic"
author: "Asish Kumar Ghosh"
date: "2020-11-30"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro to the tidyverse

## Challenge 1
Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highes revenue? Replace your bike_orderlines_wrangled_tbl object with the newly wrangled object (with the columns state and city).

## Challenge 2

Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.

## Adding the Code

```{r, code=readLines("sales_analysis_ex1.R")}
```

# Data Acquisition

## Challenge 1
Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service. You just have to google them. You can use whatever service you want. For example, you can get data about your listening history (spotify), get data about flights (skyscanner) or just check the weather forecast.

### Adding the Code

```{r, code=readLines("Data_acquisition_exercise1.R")}
```


## Challenge 2

Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category. Use the selectorgadget to get a good understanding of the website structure.

### Adding the Code

```{r, code=readLines("Data_acquisition_exercise2.R")}
```


When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.