---
title: "Business Data Science Basic"
author: "Asish Kumar Ghosh"
date: "2020-11-30"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro to the tidyverse

## Challenge 1
Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highes revenue? Replace your bike_orderlines_wrangled_tbl object with the newly wrangled object (with the columns state and city).

## Challenge 2

Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.

## Adding the Code

```{r, code=readLines("sales_analysis_ex1.R")}
```

# Data Acquisition

## Challenge 1
Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service. You just have to google them. You can use whatever service you want. For example, you can get data about your listening history (spotify), get data about flights (skyscanner) or just check the weather forecast.

### Adding the Code

```{r, code=readLines("Data_acquisition_exercise1.R")}
```


## Challenge 2

Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category. Use the selectorgadget to get a good understanding of the website structure.

### Adding the Code

```{r, code=readLines("Data_acquisition_exercise2.R")}
```


# Data Wrangling

## Challenge 1
Patent Dominance: What US company / corporation has the most patents? List the 10 US companies with the most assigned/granted patents.

## Challenge 2

Recent patent acitivity: What US company had the most patents granted in 2019? List the top 10 companies with the most new granted patents for 2019.

## Challenge 3

Innovation in Tech: What is the most innovative tech sector? For the top 10 companies (worldwide) with the most patents, what are the top 5 USPTO tech main classes?

## Adding the Code

```{r, code=readLines("Data_wrangling_exercise_data.R")}
```


# Data Visualization

## Challenge 1
Map the time course of the cumulative Covid-19 cases!

## Challenge 2

Visualize the distribution of the mortality rate (deaths / population) with geom_map(). 

## Adding the Code
